\begin{thebibliography}{99}
    \bibitem{default} Publicaciones utilizadas en el estudio y desarrollo del trabajo.
        Hay que utilizar un sistema internacional para referencias bibliográficas, de acuerdo con las indicaciones del tutor. Por ejemplo, el \href{https://www.etsiinf.upm.es/docs/estudios/grado/1475_ieeecitationref.pdf}{\textbf{sistema de IEEE}}.
    \bibitem{spanish}A. de Le{\'o}n, V. Saquicela, LM. Vilches-Bl{\'a}zquez, B. Villaz{\'o}n-Terrazas, F. Priyatna and Oscar Corcho,
        \href{http://oa.upm.es/6167/}{``Geographical Linked Data: a Spanish Use Case'',}
        in \textit{Proceedings of the In I-SEMANTICS '10  6th International Conference on Semantic Systems}
    \bibitem{toolbox}Espinoza-Arias, P., García-Delgado, M., Corcho, O. et al.
        \href{https://doi.org/10.1186/s40965-019-0060-4}{``A sustainable process and toolbox for geographical linked data generation and publication: a case study with BTN100.''},
        in \textit{Open geospatial data, softw. stand. 4, 2 (2019).}
    \bibitem{ogc-whitepaper} OGC,
        \href{portal.opengeospatial.org/files/?artifact_id=6207&ei=haJwVY7ZOcfusAXb4oK4DA&usg=AFQjCNEKzXyIOXuYNii4cRrwGU6wfD4BgQ&sig2=41F6mU19BEdW_td2wCIrIQ&bvm=bv.94911696,d.b2w}{``OGC’s Role in the Spatial Standards World''},
        in \textit{An Open GIS Consortium (OGC) White Paper}
    \bibitem{gis-standards}OGC, ISO, TC/ 211, IHO,
        \href{http://ggim.un.org/meetings/GGIM-committee/8th-Session/documents/Standards_Guide_2018.pdf}{``A Guide to the Role of Standards in Geospatial Information Management''},
        in \textit{Fifth Session of the United Nations Committee of Experts on Global Geospatial Information Management (UN-GGIM). Held from 3-7 August 2015 at the United Nations Headquarters in New York.}
    \bibitem{ogc-members}Miembros del OGC,
        \href{https://www.ogc.org/ogc/members}{``https://www.ogc.org/ogc/members''},
    \bibitem{ign} Web de datos del Instituto Geográfico Nacional,
        \href{http://datos.ign.es/}{http://datos.ign.es/}
    \bibitem{map4rdf-paper} Leon, Alexander de; Wisniewki, Filip; Villazón-Terrazas, Boris y Corcho, Oscar
        \href{http://oa.upm.es/14511/}{`` Map4rdf - Faceted Browser for Geospatial Datasets''},
        in \textit{PMOD workshop, 2012}
    \bibitem{map4rdf}Web de Map4rdf
        \href{https://oeg-upm.github.io/map4rdf/}{``https://oeg-upm.github.io/map4rdf/''},
    \bibitem{shapefile-paper}
        \href{https://support.esri.com/en/white-paper/279}{``ESRI Shapefile Technical Description''},
        \textit{An ESRI White Paper—July 1998}
    \bibitem{shapefile-specs} ESRI, 
        \href{http://webhelp.esri.com/arcgisdesktop/9.3/index.cfm?TopicName=Geoprocessing\%20considerations\%20for\%20shapefile\%20output}{``Geoprocessing considerations for shapefile output''},
        \textit{Arcgis Desktop 9.3 Help}
    \bibitem{geopackage-spec}OGC® GeoPackage Encoding Standard 1.3
        \href{http://www.geopackage.org/spec/}{``http://www.geopackage.org/spec/''},
    \bibitem{berners-lee} Tim Berners-Lee 
        \href{https://www.w3.org/DesignIssues/LinkedData.html}{``Linked Data Design Issues''},
        in \textit{W3C 2009}
    \bibitem{shapefile-no} Aurelio Morales
        \href{https://mappinggis.com/2018/08/di-no-al-shapefile-y-si-al-geopackage/}{``Di no al Shapefile y sí al GeoPackage''},
        in \textit{mappingis.com 2018}
    \bibitem{coordenadas} ESRI ArcMap 10.8 Docs,
        \href{https://desktop.arcgis.com/es/arcmap/latest/map/projections/what-are-map-projections.htm}{``¿Qué son las proyecciones cartográficas?''},
        in \textit{https://desktop.arcgis.com/es/arcmap/latest/map/projections/what-are-map-projections.htm}
    \bibitem{rtree} Antonin Guttman
        \href{https://dl.acm.org/doi/10.1145/602259.602266}{``1984. R-trees: a dynamic index structure for spatial searching''},
        in \textit{Proceedings of the 1984 ACM SIGMOD }
    \bibitem{plantilla}ab
        \href{}{``cd''},
        in \textit{ef}



\end{thebibliography}
